---
title: "World's Tallest Freestanding Structures"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(stringr)
library(rvest)
library(maps)
library(mapdata)
library(ggrepel)
library(gganimate)
library(ggplot2)

source("tallest_structures_code.R")
#load("dat.RData")
```

Data on the world's tallest buildings was scraped from the Wikipedia page: [List of tallest freestanding structures](https://en.wikipedia.org/wiki/List_of_tallest_freestanding_structures), manipulated and visualized in three plots to gain practice in R with web scraping, string processing, tidying, and data visualization^[The rvest package was used for scraping; the stringr and tidyverse packages were used for parsing and tidying; ggplot2, maps, mapdata, ggrepel, and gganimate were used for visualization.].

The retrieved data set includes all freestanding structures taller than 350 m across the world. Three plots were made to highlight some of the features of the data. The first plot is a time animation that presents the locations of the structures on year of completion:

```{r animated plot, echo = FALSE, fig.width=10, fig.height=5}

world <- map_data("world")
world$region[which(world$region=="USA")] <- "United States" # use same country name as scraped data
worldplot <- ggplot(world) + geom_polygon(aes(long, lat, group = group), 
  fill = "lightgrey", color = "white") + coord_fixed(xlim = c(-160, 165), 
  ylim = c(-50,75), ratio = 1.3) + theme_void()

map <- worldplot + geom_point(data = tall, aes(Longitude, Latitude, 
  size = Height, color = Region), alpha = 0.3) + labs(size = 'Height (m)') + 
  theme_void() + guides(size = guide_legend(reverse = T)) + 
  guides(color = guide_legend(override.aes = list(size = 5)))

anim <- worldplot + 
  geom_point(data = tall, aes(Longitude, Latitude, size = Height), 
  color = "blue", alpha = 0.3) + labs(size = 'Height (m)') + 
  guides(size = guide_legend(reverse = T)) + 
  transition_manual(tall$Year, cumulative = TRUE) + ggtitle("{current_frame}") + 
  guides(color = guide_legend(override.aes = list(size = 8))) 

animate(anim,  height = 500, width = 1000, res = 100, 
  renderer = gifski_renderer(), fps = 4)
```


The second plot illustrates three distinct time-geographic trends: 1) prior to 1980, all structures in the data set were located in North America and Europe; 2) almost all structures completed in the 1980s were in Central Asia and Russia; 3) from 1990 onward, construction of new structures was strongly dominated by countries in East Asian and the Middle East.

```{r era  plot, fig.width=10, fig.height = 5}
worldplot + geom_point(data = tall, aes(Longitude, Latitude, size = Height, 
  color = Era), alpha = 0.5) + labs(size = 'Height (m)') + 
  guides(size = guide_legend(reverse = T)) + 
  guides(color = guide_legend(override.aes = list(size = 5))) 
```

The final plot shows the number of structures taller than 350 m by country.

```{r density plot, fig.width = 10, fig.height = 5}

total_num_structures <- tall %>% mutate(region = Country) %>% group_by(region) %>% # count the structures per country
  summarize(total = n()) %>% mutate(info = paste(region, total, sep = " - "))

total_structures_map_dat <- total_num_structures %>% inner_join(world, by = "region") # join with world data

region_labels_info <- total_structures_map_dat %>% group_by(region) %>% 
  summarize(info = first(info), long = mean(long), lat = mean(lat))

region_labels_info[which(region_labels_info$region == "United States"), c("long", "lat")] <- 
  tall[first(which(tall$City == "Chicago")), c("Longitude", "Latitude")]

worldplot + geom_polygon(data = total_structures_map_dat, aes(long, lat, group = group, fill = total), color = "white") + 
  geom_text_repel(data = region_labels_info, aes(long, lat, label = info), box.padding = .45) + 
  coord_fixed(xlim = c(-160, 165), ylim = c(-50,75), ratio = 1.3) +
  scale_fill_gradient(low = "papayawhip", high = "navajowhite3", trans = "log10", name = "Structures \n above 350 m")
```

